Improved Bounds for Online Balanced Repartitioning

### 2020-04-22 paper/disc20clustering.tex
Migration graph path bound

\begin{theorem}
  \label{th:cascade-paths}
  Consider a single repartition of DET2 caused by node merge.
  There exists a sequence of node migrations that realizes this repartition, where each node-disjoint cycle has length at most $k$.
\end{theorem}

\begin{proof}
  Assume that there exists a cluster reconfiguration

Proof by contradiction.
We call a sequence of node migrations that realize the repartition \emph{a solution to repartition}.
Assume that each cost-optimal solution to repartition contains a cycle of length at least $k+1$.

Fix a solution to repartition that has the shortest length of the longest cycle, and has the least edge-disjoint cycles of such length.

>>>>

\begin{theorem}
  \label{th:cascade-paths}
  Consider a single merge action of \TAlg.
  There exists an optimal cost reconfiguration with the migration graph, where each path have length at most $k$.
\end{theorem}

\begin{proof}
  Assume the contrary, i.e., for each optimal cluster reconfiguration, its migration graph contains a path at least $k+1$.

Fix a reconfiguration and its migration graph that has the shortest length $L$ of the longest path, and has the least number of paths of length $L$.
Let $p = \lbrace v_1, v_2, \ldots, v_L \rbrace$ be any path of length $L$.
